Paper_analyses

### 2021-11-10 Paper_Analyses_subj_obje_arousal.Rmd
back to it
Today the goal is to run inferential PCAS and maybe BADIA

tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
View(tmp_df4_timeseries_345_356)

@@

@@

# 348 to 355 are missing pratice
table(is.na(db_full6new_hr_fix_stim_nt1$BIO_CDA.nSCR))
db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
  # mutate()
  group_by(as.numeric(ssid_num), as.numeric(tNo)) %>%
  arrange(ssid_num, as.numeric(tNo),as.numeric(screencontent_no))%>%
  # select(ssid, tNo,screencontent_no, Bio_Mean_HR,Bio_Mean_HR_fix)
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

@@

db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  # subset(ssid_num<500)%>%
  # group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+

@@

  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif_stim), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
  geom_smooth( method=lm, se=FALSE, linetype="dashed",
             color="darkred", size = 2)+
  stat_summary(geom = 'pointrange', pch = 1)+
    ggpubr::stat_cor()+

>>>>

tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")

unique(tmp_df4_timeseries_345_356$ssid)
View(tmp_df4_timeseries_345_356)

@@

colnames(db_HR_bio_final_346_355_withfix)

@@

# 348 to 355 are missing pratice
table(is.na(db_full6new_hr_fix_stim_nt1$BIO_CDA.nSCR))

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
  # mutate()
  group_by(as.numeric(ssid_num), as.numeric(tNo)) %>%
  arrange(ssid_num, as.numeric(tNo),as.numeric(screencontent_no))%>%
  # select(ssid, tNo,screencontent_no, Bio_Mean_HR,Bio_Mean_HR_fix)
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

@@

db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  # subset(ssid_num<500)%>%
  # group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
  group_by(ssid, stimIAPS)%>%
  # mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+

@@

  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
  geom_smooth( method=lm, se=FALSE, linetype="dashed",
             color="darkred", size = 2)+
  stat_summary(geom = 'pointrange', pch = 1)+
    # ggpubr::stat_cor()+
